---
title: "grm_tables"
output: pdf_document
---

################# SET UP #################
```{r}
setwd('/Users/asad/drive/Desktop/EEB498/permutation_tests')
library(tidyverse)
library(readxl)
library(qvalue)
```

################# READ IN DATA #################
```{r}

  ### Read p-values in from true genome scan ###
p_nogrm_true <- read_csv('/Users/asad/Drive/Desktop/EEB498/genome_scan/p_nogrm_true.csv', col_names = FALSE)

   ### Read p-values from model without grm ###
nogrm_p_list <- list.files(pattern = 'nogrm_p')
nogrm_p <- read_csv(nogrm_p_list[1], col_names = FALSE, col_types = cols())

for (i in 2:60){
  temp <- read_csv(nogrm_p_list[i], col_names = FALSE, col_types = cols())
  nogrm_p <- rbind(nogrm_p, temp)
}


    ### Read test statistic from model without grm ###
nogrm_d_list <- list.files(pattern = 'nogrm_d')
nogrm_d <- read_csv(nogrm_d_list[1], col_names = FALSE, col_types = cols())

for (i in 2:60){
  temp <- read_csv(nogrm_d_list[i], col_names = FALSE, col_types = cols())
  nogrm_d <- rbind(nogrm_d, temp)
}

```


######## DESIGN OUTPUT TABLES ###########
```{r}
sav_df <- as.data.frame(matrix(nrow = 7, ncol = 5))
sav_df$V1 <- c('SA Axis Vial', 'p <= 0.001', 'p <= 0.01', 'p <= 0.05', 'Q <= 0.1', 'Q <= 0.2', 'Q <= 0.3')
sav_df[1,2:5] <- c('Number of Blocks', 'Proportion of Permutations with as many or more blocks', 'Number of 1 Mb clusters', 'Proportion of Permutations with as many or more 1 Mb clusters')

sac_df <- as.data.frame(matrix(nrow = 7, ncol = 5))
sac_df$V1 <- c('SA Axis Cage', 'p <= 0.001', 'p <= 0.01', 'p <= 0.05', 'Q <= 0.1', 'Q <= 0.2', 'Q <= 0.3')
sac_df[1,2:5] <- c('Number of Blocks', 'Proportion of Permutations with as many or more blocks', 'Number of 1 Mb clusters', 'Proportion of Permutations with as many or more 1 Mb clusters')

scv_df <- as.data.frame(matrix(nrow = 7, ncol = 5))
scv_df$V1 <- c('SC Axis Vial', 'p <= 0.001', 'p <= 0.01', 'p <= 0.05', 'Q <= 0.1', 'Q <= 0.2', 'Q <= 0.3')
scv_df[1,2:5] <- c('Number of Blocks', 'Proportion of Permutations with as many or more blocks', 'Number of 1 Mb clusters', 'Proportion of Permutations with as many or more 1 Mb clusters')

scc_df <- as.data.frame(matrix(nrow = 7, ncol = 5))
scc_df$V1 <- c('SC Axis Cage', 'p <= 0.001', 'p <= 0.01', 'p <= 0.05', 'Q <= 0.1', 'Q <= 0.2', 'Q <= 0.3')
scc_df[1,2:5] <- c('Number of Blocks', 'Proportion of Permutations with as many or more blocks', 'Number of 1 Mb clusters', 'Proportion of Permutations with as many or more 1 Mb clusters')

```

### Fill in Number of Blocks for each SA and SC Trait
```{r}

# SEXUAL ANTAGONISM VIAL

#Collect all p-values for every 7th block for the trait
sav_true <- p_nogrm_true %>%
  filter(.[1] == 'sa.axis.vial') %>%
  as.numeric(.[1,2:1683]) %>%
  na.omit(.)

#Get number of blocks under each threshold
sav_0.1_t <- length(sav_true[sav_true <= 0.1])
sav_0.05_t <- length(sav_true[sav_true <= 0.05])
sav_0.01_t <- length(sav_true[sav_true <= 0.01])
sav_0.001_t <- length(sav_true[sav_true <= 0.001])

sav_q_0.3_t <- length(qvalue(sav_true)$qvalues[qvalue(sav_true)$qvalues <= 0.3])
sav_q_0.2_t <- length(qvalue(sav_true)$qvalues[qvalue(sav_true)$qvalues <= 0.2])
sav_q_0.1_t <- length(qvalue(sav_true)$qvalues[qvalue(sav_true)$qvalues <= 0.1])

#Put into respective df for each trait
sav_df[2:7, 2] <- c(sav_0.001_t, sav_0.01_t, sav_0.05_t, sav_q_0.1_t, sav_q_0.2_t, sav_q_0.3_t)

# SEXUAL CONCORDANCE VIAL

scv_true <- p_nogrm_true %>%
  filter(.[1] == 'sc.axis.vial') %>%
  as.numeric(.[1,2:1683]) %>%
  na.omit(.)

scv_0.1_t <- length(scv_true[scv_true <= 0.1])
scv_0.05_t <- length(scv_true[scv_true <= 0.05])
scv_0.01_t <- length(scv_true[scv_true <= 0.01])
scv_0.001_t <- length(scv_true[scv_true <= 0.001])

scv_q_0.3_t <- length(qvalue(scv_true)$qvalues[qvalue(scv_true)$qvalues <= 0.3])
scv_q_0.2_t <- length(qvalue(scv_true)$qvalues[qvalue(scv_true)$qvalues <= 0.2])
scv_q_0.1_t <- length(qvalue(scv_true)$qvalues[qvalue(scv_true)$qvalues <= 0.1])

scv_df[2:7, 2] <- c(scv_0.001_t, scv_0.01_t, scv_0.05_t, scv_q_0.1_t, scv_q_0.2_t, scv_q_0.3_t)

# SEXUAL ANTAGONISM CAGE

sac_true <- p_nogrm_true %>%
  filter(.[1] == 'sa.axis.cage') %>%
  as.numeric(.[1,2:1683]) %>%
  na.omit(.)

sac_0.1_t <- length(sac_true[sac_true <= 0.1])
sac_0.05_t <- length(sac_true[sac_true <= 0.05])
sac_0.01_t <- length(sac_true[sac_true <= 0.01])
sac_0.001_t <- length(sac_true[sac_true <= 0.001])

sac_q_0.3_t <- length(qvalue(sac_true)$qvalues[qvalue(sac_true)$qvalues <= 0.3])
sac_q_0.2_t <- length(qvalue(sac_true)$qvalues[qvalue(sac_true)$qvalues <= 0.2])
sac_q_0.1_t <- length(qvalue(sac_true)$qvalues[qvalue(sac_true)$qvalues <= 0.1])

sac_df[2:7, 2] <- c(sac_0.001_t, sac_0.01_t, sac_0.05_t, sac_q_0.1_t, sac_q_0.2_t, sac_q_0.3_t)

#SEXUAL CONCORDANCE CAGE

scc_true <- p_nogrm_true %>%
  filter(.[1] == 'sc.axis.cage') %>%
  as.numeric(.[1,2:1683]) %>%
  na.omit(.)

scc_0.1_t <- length(scc_true[scc_true <= 0.1])
scc_0.05_t <- length(scc_true[scc_true <= 0.05])
scc_0.01_t <- length(scc_true[scc_true <= 0.01])
scc_0.001_t <- length(scc_true[scc_true <= 0.001])

scc_q_0.3_t <- length(qvalue(scc_true)$qvalues[qvalue(scc_true)$qvalues <= 0.3])
scc_q_0.2_t <- length(qvalue(scc_true)$qvalues[qvalue(scc_true)$qvalues <= 0.2])
scc_q_0.1_t <- length(qvalue(scc_true)$qvalues[qvalue(scc_true)$qvalues <= 0.1])

scc_df[2:7, 2] <- c(scc_0.001_t, scc_0.01_t, scc_0.05_t, scc_q_0.1_t, scc_q_0.2_t, scc_q_0.3_t)

```

##### FILL IN PROPORTION OF PERMUTATIONS WITH AS MANY OR MORE BLOCKS
```{r}
model <- nogrm_p # with or without GRM

perm_no <- length(grm_p$X1)/8
## SA Axis Cage ##


sac_p_df <- model %>%
  filter(model[2] == 'sa.axis.cage')


sac_p_0.1 <- vector(length = perm_no)
sac_p_0.05 <- vector(length = perm_no)
sac_p_0.01 <- vector(length = perm_no)
sac_p_0.001 <- vector(length = perm_no)
sac_q_0.3 <- vector(length = perm_no)
sac_q_0.2 <- vector(length = perm_no)
sac_q_0.1 <- vector(length = perm_no)

for(perm in 1:nrow(sac_p_df)){
  
  temp <- as.numeric(sac_p_df[perm,3:1684])
  temp_q <- qvalue(as.numeric(sac_p_df[perm,3:1684]))$qvalues
  
  sac_p_0.1[perm] <- length(temp[temp <= 0.1])
  sac_p_0.05[perm] <- length(temp[temp <= 0.05])
  sac_p_0.01[perm] <- length(temp[temp <= 0.01])
  sac_p_0.001[perm] <- length(temp[temp <= 0.001])
  
  sac_q_0.3[perm] <- length(temp_q[temp_q <= 0.3])
  sac_q_0.2[perm] <- length(temp_q[temp_q <= 0.2])
  sac_q_0.1[perm] <- length(temp_q[temp_q <= 0.1])
}

sac_df[2, 3] <- round(length(sac_p_0.001[sac_p_0.001 >= sac_0.001_t])/perm_no, 4)
sac_df[3, 3] <- round(length(sac_p_0.01[sac_p_0.01 >= sac_0.01_t])/perm_no, 4)
sac_df[4, 3] <- round(length(sac_p_0.05[sac_p_0.05 >= sac_0.05_t])/perm_no, 4)
sac_df[5, 3] <- round(length(sac_q_0.1[sac_q_0.1 >= sac_q_0.1_t])/perm_no, 4)
sac_df[6, 3] <- round(length(sac_q_0.2[sac_q_0.2 >= sac_q_0.2_t])/perm_no, 4)
sac_df[7, 3] <- round(length(sac_q_0.3[sac_q_0.3 >= sac_q_0.3_t])/perm_no, 4)

#Finish for Q Values

## SC Axis Cage ##

scc_p_df <- model %>%
  filter(model[2] == 'sc.axis.cage')


scc_p_0.1 <- vector(length = perm_no)
scc_p_0.05 <- vector(length = perm_no)
scc_p_0.01 <- vector(length = perm_no)
scc_p_0.001 <- vector(length = perm_no)
scc_q_0.3 <- vector(length = perm_no)
scc_q_0.2 <- vector(length = perm_no)
scc_q_0.1 <- vector(length = perm_no)


for(perm in 1:nrow(scc_p_df)){
  
  temp <- as.numeric(scc_p_df[perm,3:1684])
  temp_q <- qvalue(as.numeric(scc_p_df[perm,3:1684]))$qvalues
  
  scc_p_0.1[perm] <- length(temp[temp <= 0.1])
  scc_p_0.05[perm] <- length(temp[temp <= 0.05])
  scc_p_0.01[perm] <- length(temp[temp <= 0.01])
  scc_p_0.001[perm] <- length(temp[temp <= 0.001])
  
  scc_q_0.3[perm] <- length(temp_q[temp_q <= 0.3])
  scc_q_0.2[perm] <- length(temp_q[temp_q <= 0.2])
  scc_q_0.1[perm] <- length(temp_q[temp_q <= 0.1])
}


scc_df[2, 3] <- round(length(scc_p_0.001[scc_p_0.001 >= scc_0.001_t])/perm_no, 4)
scc_df[3, 3] <- round(length(scc_p_0.01[scc_p_0.01 >= scc_0.01_t])/perm_no, 4)
scc_df[4, 3] <- round(length(scc_p_0.05[scc_p_0.05 >= scc_0.05_t])/perm_no, 4)
scc_df[5, 3] <- round(length(scc_q_0.1[scc_q_0.1 >= scc_q_0.1_t])/perm_no, 4)
scc_df[6, 3] <- round(length(scc_q_0.2[scc_q_0.2 >= scc_q_0.2_t])/perm_no, 4)
scc_df[7, 3] <- round(length(scc_q_0.3[scc_q_0.3 >= scc_q_0.3_t])/perm_no, 4)

## SA Axis Vial ##

sav_p_df <- model %>%
  filter(model[2] == 'sa.axis.vial')

sav_p_0.1 <- vector(length = perm_no)
sav_p_0.05 <- vector(length = perm_no)
sav_p_0.01 <- vector(length = perm_no)
sav_p_0.001 <- vector(length = perm_no)
sav_q_0.3 <- vector(length = perm_no)
sav_q_0.2 <- vector(length = perm_no)
sav_q_0.1 <- vector(length = perm_no)

for(perm in 1:nrow(sav_p_df)){
  
  temp <- as.numeric(sav_p_df[perm,3:1684])
  temp_q <- qvalue(as.numeric(sav_p_df[perm,3:1684]))$qvalues
  
  sav_p_0.1[perm] <- length(temp[temp <= 0.1])
  sav_p_0.05[perm] <- length(temp[temp <= 0.05])
  sav_p_0.01[perm] <- length(temp[temp <= 0.01])
  sav_p_0.001[perm] <- length(temp[temp <= 0.001])
  
  sav_q_0.3[perm] <- length(temp_q[temp_q <= 0.3])
  sav_q_0.2[perm] <- length(temp_q[temp_q <= 0.2])
  sav_q_0.1[perm] <- length(temp_q[temp_q <= 0.1])
}

sav_df[2, 3] <- round(length(sav_p_0.001[sav_p_0.001 >= sav_0.001_t])/perm_no, 4)
sav_df[3, 3] <- round(length(sav_p_0.01[sav_p_0.01 >= sav_0.01_t])/perm_no, 4)
sav_df[4, 3] <- round(length(sav_p_0.05[sav_p_0.05 >= sav_0.05_t])/perm_no, 4)
sav_df[5, 3] <- round(length(sav_q_0.1[sav_q_0.1 >= sav_q_0.1_t])/perm_no, 4)
sav_df[6, 3] <- round(length(sav_q_0.2[sav_q_0.2 >= sav_q_0.2_t])/perm_no, 4)
sav_df[7, 3] <- round(length(sav_q_0.3[sav_q_0.3 >= sav_q_0.3_t])/perm_no, 4)

## SC Axis Vial ##

scv_p_df <- model %>%
  filter(model[2] == 'sc.axis.vial')

scv_p_0.1 <- vector(length = perm_no)
scv_p_0.05 <- vector(length = perm_no)
scv_p_0.01 <- vector(length = perm_no)
scv_p_0.001 <- vector(length = perm_no)
scv_q_0.3 <- vector(length = perm_no)
scv_q_0.2 <- vector(length = perm_no)
scv_q_0.1 <- vector(length = perm_no)

for(perm in 1:nrow(scv_p_df)){
  
  temp <- as.numeric(scv_p_df[perm,3:1684])
  temp_q <- qvalue(as.numeric(scv_p_df[perm,3:1684]))$qvalues
  
  scv_p_0.1[perm] <- length(temp[temp <= 0.1])
  scv_p_0.05[perm] <- length(temp[temp <= 0.05])
  scv_p_0.01[perm] <- length(temp[temp <= 0.01])
  scv_p_0.001[perm] <- length(temp[temp <= 0.001])
  
  scv_q_0.3[perm] <- length(temp_q[temp_q <= 0.3])
  scv_q_0.2[perm] <- length(temp_q[temp_q <= 0.2])
  scv_q_0.1[perm] <- length(temp_q[temp_q <= 0.1])
}

scv_df[2, 3] <- round(length(scv_p_0.001[scv_p_0.001 >= scv_0.001_t])/perm_no, 4)
scv_df[3, 3] <- round(length(scv_p_0.01[scv_p_0.01 >= scv_0.01_t])/perm_no, 4)
scv_df[4, 3] <- round(length(scv_p_0.05[scv_p_0.05 >= scv_0.05_t])/perm_no, 4)
scv_df[5, 3] <- round(length(scv_q_0.1[scv_q_0.1 >= scv_q_0.1_t])/perm_no, 4)
scv_df[6, 3] <- round(length(scv_q_0.2[scv_q_0.2 >= scv_q_0.2_t])/perm_no, 4)
scv_df[7, 3] <- round(length(scv_q_0.3[scv_q_0.3 >= scv_q_0.3_t])/perm_no, 4)


# sac_df[2,3] <-round(length(sac_p_0.1[sac_p_0.1 >= sac_0.1_t])/perm_no, 4)
# scc_df[2,3] <-round(length(scc_p_0.1[scc_p_0.1 >= scc_0.1_t])/perm_no, 4)
# sav_df[2,3] <-round(length(sav_p_0.1[sav_p_0.1 >= sav_0.1_t])/perm_no, 4)
# scv_df[2,3] <-round(length(scv_p_0.1[scv_p_0.1 >= scv_0.1_t])/perm_no, 4)


```
### Graph p <= 0.05
```{r}
ggplot() + geom_histogram(aes(x = sac_p_0.05)) + 
  geom_vline(xintercept = sac_0.05_t) + 
  xlab('No. of blocks p <= 0.05') + ylab('No. of permutations') + 
  annotate('text', x = 200, y = 100, size = 7, label = paste('p <=', sac_df[4, 3] )) + 
  ggtitle('SA Cage')

ggplot() + geom_histogram(aes(x = scc_p_0.05)) + 
  geom_vline(xintercept = scc_0.05_t) + 
  xlab('No. of blocks p <= 0.05') + ylab('No. of permutations') + 
  annotate('text', x = 200, y = 100, size = 7, label = paste('p <=', scc_df[4, 3] )) + 
  ggtitle('SC Cage')

ggplot() + geom_histogram(aes(x = sav_p_0.05)) + 
  geom_vline(xintercept = sav_0.05_t) + 
  xlab('No. of blocks p <= 0.05') + ylab('No. of permutations') + 
  annotate('text', x = 200, y = 100, size = 7, label = paste('p <=', sav_df[4, 3] )) + 
  ggtitle('SA Vial')

ggplot() + geom_histogram(aes(x = scv_p_0.05)) + 
  geom_vline(xintercept = scv_0.05_t) + 
  xlab('No. of blocks p <= 0.05') + ylab('No. of permutations') + 
  annotate('text', x = 200, y = 100, size = 7, label = paste('p <=', scv_df[4, 3] )) + 
  ggtitle('SC Vial')
```

### Get list of chromosomes and create vector of chr
```{r}
#Get list of chromosomes for every 7th block
chr <- vector(length = 1681)

#Iterative variable by which we can fill chr
a = 1

#Temporary dataframe with less memory usage by which to extract chromosome from which block is on
HMM_matrix_temp <- HMM_matrix %>%
  filter(.$RILID == 11002)

#Fill chr
for(i in seq(1, 11768, 7)){

  chr[a] <- HMM_matrix_temp$Chr[HMM_matrix_temp$row.id == unique(HMM_matrix_temp$row.id)[i]]
  
  a = a + 1
}

```

##GET CLUSTERS IN REAL DATA FOR P-VALUES
```{r}
#Get list of traits
traits <- unique(grm_p$X2)[5:8]
#Choose a window size
window.size = 14
# Pvalue cutoff
cutoffs_p = c(0.001, 0.01, 0.05)
#Get chr arms
chr.arms = c("X", "2L", "2R", "3L", "3R")

output.df.real.p <- as.data.frame(matrix(nrow = 3, ncol = 4))
colnames(output.df.real.p) <- traits

for(value in 1:length(cutoffs_p)){

  #For loop per trait
  for(n in 1:length(traits)){
    
    #Choose data from models without grm
    grm_p_temp <- p_nogrm_true %>%
      filter(X1 == traits[n])
    
    
    #For loop per permutation
    for(p in 1:nrow(grm_p_temp)){
      
      #Organize data from permutation for cluster analysis
      permutation <- bind_cols(chr = chr, 
                            pvalue = as.numeric((grm_p_temp)[1,2:1683]),
                            pos.index = seq(1, 11768, 7))
      
      n_clusters <- 0
      
        for(arm in chr.arms){
          
          permutation.tmp = permutation %>%
          filter(chr == arm) %>%
          filter(pvalue <= cutoffs_p[value])
          
          if(nrow(permutation.tmp) > 1){
            
              n_clusters <- n_clusters + 1
            
                    for(i in 1:(nrow(permutation.tmp)-1)){
                      
                      blocks_apart <- permutation.tmp$pos.index[i + 1] - permutation.tmp$pos.index[i]
                      
                      if (blocks_apart < window.size) {
                        
                        n_clusters <- n_clusters
                        
                      } else {
                        
                        n_clusters = n_clusters + 1
                      }
                      
                    }
            
          } else if(nrow(permutation.tmp) == 1){
            
            n_clusters <- n_clusters + 1
          
          } else {
            
            n_clusters <- n_clusters
            
          }
      
        } 
  
      output.df.real.p[value, n] <- n_clusters
    }
  }
}

sac_df[2:4,4] <- output.df.real.p[1]
scc_df[2:4,4] <- output.df.real.p[2]
sav_df[2:4,4] <- output.df.real.p[3]
scv_df[2:4,4] <- output.df.real.p[4]

```

##GET CLUSTERS IN REAL DATA FOR Q-VALUES
```{r}
#Get list of traits
traits <- unique(nogrm_p$X2)[5:8]
#Choose a window size
window.size = 14
# Pvalue cutoff
cutoffs_q = c(0.1, 0.2, 0.3)
#Get chr arms
chr.arms = c("X", "2L", "2R", "3L", "3R")

output.df.real.q <- as.data.frame(matrix(nrow = 3, ncol = 4))
colnames(output.df.real.q) <- traits

for(value in 1:length(cutoffs_q)){

  #For loop per trait
  for(n in 1:length(traits)){
    
    #Choose data from model
    p_temp <- p_nogrm_true %>%
      filter(X1 == traits[n])
    
    
    #For loop per permutation
    for(p in 1:nrow(p_temp)){
      
      #Organize data from permutation for cluster analysis
      permutation <- bind_cols(chr = chr, 
                            qvalue = qvalue(as.numeric((grm_p_temp)[1,2:1683]))$qvalues,
                            pos.index = seq(1, 11768, 7))
      
      n_clusters <- 0
      
        for(arm in chr.arms){
          
          permutation.tmp = permutation %>%
          filter(chr == arm) %>%
          filter(qvalue <= cutoffs_q[value])
          permutation.tmp
          
          if(nrow(permutation.tmp) > 1){
            
              n_clusters <- n_clusters + 1
            
                    for(i in 1:(nrow(permutation.tmp)-1)){
                      
                      blocks_apart <- permutation.tmp$pos.index[i + 1] - permutation.tmp$pos.index[i]
                      
                      if (blocks_apart < window.size) {
                        
                        n_clusters <- n_clusters
                        
                      } else {
                        
                        n_clusters = n_clusters + 1
                      }
                      
                    }
            
          } else if(nrow(permutation.tmp) == 1){
            
            n_clusters <- n_clusters + 1
          
          } else {
            
            n_clusters <- n_clusters
            
          }
      
        } 
  
      output.df.real.q[value, n] <- n_clusters
    }
  }
}

sac_df[5:7,4] <- output.df.real.q[1]
scc_df[5:7,4] <- output.df.real.q[2]
sav_df[5:7,4] <- output.df.real.q[3]
scv_df[5:7,4] <- output.df.real.q[4]

```


### GET CLUSTERS FROM PERMUTATION TESTS FOR P-VALUES
```{r}
#Get list of traits
traits <- unique(nogrm_p$X2)[5:8]
#Choose a window size
window.size = 14
# Pvalue cutoff
cutoff_p = c(0.1)
#Get chr arms
chr.arms = c("X", "2L", "2R", "3L", "3R")

output.df.p <- as.data.frame(matrix(nrow = perm_no, ncol = 3))
colnames(output.df.p) <- c('p <= 0.001', 'p <= 0.01', 'p <= 0.05')



#For loop per trait
for(n in 1:length(cutoff_p)){
  
  #Choose data from models with or without grm
  p_temp <- nogrm_p %>%
    filter(X2 == traits[4])
  
  
  #For loop per permutation
  for(p in 1:nrow(p_temp)){
    
    #Organize data from permutation for cluster analysis
    permutation <- bind_cols(chr = chr, 
                          pvalue = as.numeric((grm_p_temp)[p,3:1684]),
                          pos.index = seq(1, 11768, 7))
    
    n_clusters <- 0
    
      for(arm in chr.arms){
        
        permutation.tmp = permutation %>%
        filter(chr == arm) %>%
        filter(pvalue <= cutoff_p[n])
        
        if(nrow(permutation.tmp) > 1){
          
            n_clusters <- n_clusters + 1
          
                  for(i in 1:(nrow(permutation.tmp)-1)){
                    
                    blocks_apart <- permutation.tmp$pos.index[i + 1] - permutation.tmp$pos.index[i]
                    
                    if (blocks_apart < window.size) {
                      
                      n_clusters <- n_clusters
                      
                    } else {
                      
                      n_clusters = n_clusters + 1
                    }
                    
                  }
          
        } else if(nrow(permutation.tmp) == 1){
          
          n_clusters <- n_clusters + 1
        
        } else {
          
          n_clusters <- n_clusters
          
        }
    
      } 

    output.df.p[p, n] <- n_clusters
  }
}

```


#We have sac_fake_df, scc_fake_df, sav_fake_df, scv_fake_df
#Now fill in last column for the p-values
```{r}
sac_df[2:4, 5] <- c(round(length(sac_fake_df[1][sac_fake_df[1] >= as.integer(sac_df[2,4])])/perm_no, 4),
                    round(length(sac_fake_df[2][sac_fake_df[2] >= as.integer(sac_df[3,4])])/perm_no, 4),
                    round(length(sac_fake_df[3][sac_fake_df[3] >= as.integer(sac_df[4,4])])/perm_no, 4))

scc_df[2:4, 5] <- c(round(length(scc_fake_df[1][scc_fake_df[1] >= as.integer(scc_df[2,4])])/perm_no, 4),
                    round(length(scc_fake_df[2][scc_fake_df[2] >= as.integer(scc_df[3,4])])/perm_no, 4),
                    round(length(scc_fake_df[3][scc_fake_df[3] >= as.integer(scc_df[4,4])])/perm_no, 4))

sav_df[2:4, 5] <- c(round(length(sav_fake_df[1][sav_fake_df[1] >= as.integer(sav_df[2,4])])/perm_no, 4),
                    round(length(sav_fake_df[2][sav_fake_df[2] >= as.integer(sav_df[3,4])])/perm_no, 4),
                    round(length(sav_fake_df[3][sav_fake_df[3] >= as.integer(sav_df[4,4])])/perm_no, 4))

scv_df[2:4, 5] <- c(round(length(scv_fake_df[1][scv_fake_df[1] >= as.integer(scv_df[2,4])])/perm_no, 4),
                    round(length(scv_fake_df[2][scv_fake_df[2] >= as.integer(scv_df[3,4])])/perm_no, 4),
                    round(length(scv_fake_df[3][scv_fake_df[3] >= as.integer(scv_df[4,4])])/perm_no, 4))
```

### GET CLUSTERS FROM PERMUTATION TESTS FOR Q-VALUES
```{r}
#Get list of traits
traits <- unique(nogrm_p$X2)[5:8]
#Choose a window size
window.size = 14
# Pvalue cutoff
cutoff_q = c(0.1, 0.2, 0.3)
#Get chr arms
chr.arms = c("X", "2L", "2R", "3L", "3R")

output.df.q <- as.data.frame(matrix(nrow = perm_no, ncol = 3))
colnames(output.df.q) <- c('q <= 0.1', 'q <= 0.2', 'q <= 0.3')



#For loop per trait
for(n in 1:length(cutoff_q)){
  
  #Choose data from models with or without grm
  p_temp <- nogrm_p %>%
    filter(X2 == traits[4])
  
  
  #For loop per permutation
  for(p in 1:nrow(p_temp)){
    
    #Organize data from permutation for cluster analysis
    permutation <- bind_cols(chr = chr, 
                          qvalue = qvalue(as.numeric((grm_p_temp)[p,3:1684]))$qvalues,
                          pos.index = seq(1, 11768, 7))
    
    n_clusters <- 0
    
      for(arm in chr.arms){
        
        permutation.tmp = permutation %>%
        filter(chr == arm) %>%
        filter(qvalue <= cutoff_q[n])
        
        if(nrow(permutation.tmp) > 1){
          
            n_clusters <- n_clusters + 1
          
                  for(i in 1:(nrow(permutation.tmp)-1)){
                    
                    blocks_apart <- permutation.tmp$pos.index[i + 1] - permutation.tmp$pos.index[i]
                    
                    if (blocks_apart < window.size) {
                      
                      n_clusters <- n_clusters
                      
                    } else {
                      
                      n_clusters = n_clusters + 1
                    }
                    
                  }
          
        } else if(nrow(permutation.tmp) == 1){
          
          n_clusters <- n_clusters + 1
        
        } else {
          
          n_clusters <- n_clusters
          
        }
    
      } 

    output.df.q[p, n] <- n_clusters
  }
}

head(output.df.q)
scv_fake_df <- output.df.q
```

#Now fill in the last column for the q-values
```{r}
sac_df[5:7, 5] <- c(round(length(sac_fake_df[1][sac_fake_df[1] >= as.integer(sac_df[5,4])])/perm_no, 4),
                    round(length(sac_fake_df[2][sac_fake_df[2] >= as.integer(sac_df[6,4])])/perm_no, 4),
                    round(length(sac_fake_df[3][sac_fake_df[3] >= as.integer(sac_df[7,4])])/perm_no, 4))

scc_df[5:7, 5] <- c(round(length(scc_fake_df[1][scc_fake_df[1] >= as.integer(scc_df[5,4])])/perm_no, 4),
                    round(length(scc_fake_df[2][scc_fake_df[2] >= as.integer(scc_df[6,4])])/perm_no, 4),
                    round(length(scc_fake_df[3][scc_fake_df[3] >= as.integer(scc_df[7,4])])/perm_no, 4))

sav_df[5:7, 5] <- c(round(length(sav_fake_df[1][sav_fake_df[1] >= as.integer(sav_df[5,4])])/perm_no, 4),
                    round(length(sav_fake_df[2][sav_fake_df[2] >= as.integer(sav_df[6,4])])/perm_no, 4),
                    round(length(sav_fake_df[3][sav_fake_df[3] >= as.integer(sav_df[7,4])])/perm_no, 4))

scv_df[5:7, 5] <- c(round(length(scv_fake_df[1][scv_fake_df[1] >= as.integer(scv_df[5,4])])/perm_no, 4),
                    round(length(scv_fake_df[2][scv_fake_df[2] >= as.integer(scv_df[6,4])])/perm_no, 4),
                    round(length(scv_fake_df[3][scv_fake_df[3] >= as.integer(scv_df[7,4])])/perm_no, 4))
```

# Get Kth Percentile p-values {k = 1, 5, 10} for each block for SA/SC Traits for the permuted data sets
```{r}
# Sexual Antagonism Cage
sac_p <- nogrm_p %>%
  filter(.[2] == 'sa.axis.cage') %>%
  select(X3:X1684)

sac_plot <- bind_cols(chr = chr, block = seq(1, 11768, 7), 
                      k_1 = vector(length = length(chr)),
                      k_5 = vector(length = length(chr)),
                      k_10 = vector(length = length(chr)))


for(block in 1:length(chr)){
    
  perm <- pull(sac_p, block)
  k <- quantile(perm, c(0.01, 0.05, 0.1))
  
  sac_plot$k_1[block] <- (-1)*log10(k[1])
  sac_plot$k_5[block] <- (-1)*log10(k[2])
  sac_plot$k_10[block] <- (-1)*log10(k[3])
  
}

# Sexual Concordance Cage
scc_p <- nogrm_p %>%
  filter(.[2] == 'sc.axis.cage') %>%
  select(X3:X1684)

scc_plot <- bind_cols(chr = chr, block = seq(1, 11768, 7), 
                      k_1 = vector(length = length(chr)),
                      k_5 = vector(length = length(chr)),
                      k_10 = vector(length = length(chr)))


for(block in 1:length(chr)){
    
  perm <- pull(scc_p, block)
  k <- quantile(perm, c(0.01, 0.05, 0.1))
  
  scc_plot$k_1[block] <- (-1)*log10(k[1])
  scc_plot$k_5[block] <- (-1)*log10(k[2])
  scc_plot$k_10[block] <- (-1)*log10(k[3])
  
}

# Sexual Antagonism Vial
sav_p <- nogrm_p %>%
  filter(.[2] == 'sa.axis.vial') %>%
  select(X3:X1684)

sav_plot <- bind_cols(chr = chr, block = seq(1, 11768, 7), 
                      k_1 = vector(length = length(chr)),
                      k_5 = vector(length = length(chr)),
                      k_10 = vector(length = length(chr)))


for(block in 1:length(chr)){
    
  perm <- pull(sav_p, block)
  k <- quantile(perm, c(0.01, 0.05, 0.1))
  
  sav_plot$k_1[block] <- (-1)*log10(k[1])
  sav_plot$k_5[block] <- (-1)*log10(k[2])
  sav_plot$k_10[block] <- (-1)*log10(k[3])
  
}

# Sexual Concordance Vial
scv_p <- nogrm_p %>%
  filter(.[2] == 'sc.axis.vial') %>%
  select(X3:X1684)

scv_plot <- bind_cols(chr = chr, block = seq(1, 11768, 7), 
                      k_1 = vector(length = length(chr)),
                      k_5 = vector(length = length(chr)),
                      k_10 = vector(length = length(chr)))


for(block in 1:length(chr)){
    
  perm <- pull(scv_p, block)
  k <- quantile(perm, c(0.01, 0.05, 0.1))
  
  scv_plot$k_1[block] <- (-1)*log10(k[1])
  scv_plot$k_5[block] <- (-1)*log10(k[2])
  scv_plot$k_10[block] <- (-1)*log10(k[3])
  
}

```

#Plot manhattan plots
```{r}
ggplot(data = sac_plot) + geom_line(aes(x = block, y = k_1), color = 'grey') + 
  geom_line(aes(x = block, y = k_5), color = 'grey') + geom_line(aes(x = block, y = k_10), color = 'grey') + 
  geom_line(aes(x = block, y = (-1)*log10(sac_true)), color = 'red') + 
  xlab('block no.') + ylab('-log10(p)') + theme_minimal() +
  ggtitle('SA Cage') + 
  annotate('text', x = c(0, 319*7, 640*7, 941*7, 1287*7), y = 4, label = unique(chr)) + 
  annotate('text', x = 12500, y = c(mean(sac_plot$k_1), mean(sac_plot$k_5), mean(sac_plot$k_10)),
           label = c('k = 1', 'k = 5', 'k = 10')) 
  
ggplot(data = scc_plot) + geom_line(aes(x = block, y = k_1), color = 'grey') + 
  geom_line(aes(x = block, y = k_5), color = 'grey') + geom_line(aes(x = block, y = k_10), color = 'grey') + 
  geom_line(aes(x = block, y = (-1)*log10(scc_true)), color = 'red') + 
  xlab('block no.') + ylab('-log10(p)') + theme_minimal() + 
  ggtitle('SC Cage') + 
  annotate('text', x = c(0, 319*7, 640*7, 941*7, 1287*7), y = 4, label = unique(chr)) + 
  annotate('text', x = 12500, y = c(mean(scc_plot$k_1), mean(scc_plot$k_5), mean(scc_plot$k_10)),
           label = c('k = 1', 'k = 5', 'k = 10')) 

ggplot(data = sav_plot) + geom_line(aes(x = block, y = k_1), color = 'grey') + 
  geom_line(aes(x = block, y = k_5), color = 'grey') + geom_line(aes(x = block, y = k_10), color = 'grey') + 
  geom_line(aes(x = block, y = (-1)*log10(sav_true)), color = 'red') + 
  xlab('block no.') + ylab('-log10(p)') + theme_minimal() + 
  ggtitle('SA Vial') + 
  annotate('text', x = c(0, 319*7, 640*7, 941*7, 1287*7), y = 4, label = unique(chr)) + 
  annotate('text', x = 12500, y = c(mean(sav_plot$k_1), mean(sav_plot$k_5), mean(sav_plot$k_10)),
           label = c('k = 1', 'k = 5', 'k = 10')) 

ggplot(data = scv_plot) + geom_line(aes(x = block, y = k_1), color = 'grey') + 
  geom_line(aes(x = block, y = k_5), color = 'grey') + geom_line(aes(x = block, y = k_10), color = 'grey') + 
  geom_line(aes(x = block, y = (-1)*log10(scv_true)), color = 'red') +
  xlab('block no.') + ylab('-log10(p)') + theme_minimal() + 
  ggtitle('SC Vial') + 
  annotate('text', x = c(0, 319*7, 640*7, 941*7, 1287*7), y = 4, label = unique(chr)) + 
  annotate('text', x = 12500, y = c(mean(scv_plot$k_1), mean(scv_plot$k_5), mean(scv_plot$k_10)),
           label = c('k = 1', 'k = 5', 'k = 10')) 
```




