---
title: "grm_tables_8traits"
output: pdf_document
---

#Load in packages

```{r}
setwd('/Users/asad/drive/Desktop/EEB498/permutation_tests')
library(tidyverse)
library(readxl)
library(qvalue)
library(cowplot)

```

#Read in data
```{r}
  ### Read p-values in from true genome scan 
p_nogrm_true <- read_csv('/Users/asad/Drive/Desktop/EEB498/genome_scan/p_nogrm_true.csv', col_names = FALSE)

   ### Read p-values from model without grm ###
nogrm_p_list <- list.files(pattern = 'nogrm_p')
nogrm_p <- read_csv(nogrm_p_list[1], col_names = FALSE, col_types = cols())

for (i in 2:60){
  temp <- read_csv(nogrm_p_list[i], col_names = FALSE, col_types = cols())
  nogrm_p <- rbind(nogrm_p, temp)
}
```


Columns:
1) Statistical requirement (i.e.., p < 0.001, p < 0.01, p < 0.05, p < 0.1, q < 0.1, q < 0.2, q < 0.3)
2) Number of blocks meeting this criteria in the unpermuted data
3) The proportion of permutations with as many or more blocks as in the unpermuted data
3) Mean - this refers to the mean across permutations for the number of blocks meeting that statistical criteria.
4) Median - as above but for median
5) 2.5 percentile value*
6) 5 percentile value*
7) 95 percentile value*
8) 97.5 percentile value*


#Set up data frame with the above columns
```{r}
traits <- unique(grm_p$X2)

df <- data.frame(p_value = c('p <= 0.001', 'p <= 0.01', 'p <= 0.05', 'p <= 0.1', 'q <= 0.1', 'q <= 0.2', 'q <= 0.3'),
                 num_blocks_real_data = vector(length = 7),
                 prop_perm_blocks_as_many_or_more = vector(length = 7),
                 mean_num_perm_blocks = vector(length = 7),
                 median_num_perm_blocks = vector(length = 7),
                 percentile_2.5_perm = vector(length = 7),
                 percentile_5_perm = vector(length = 7),
                 percentile_95_perm = vector(length = 7),
                 percentile_97.5_perm = vector(length = 7))

data_frames <- c('df_mc', 'df_mv', 'df_fc', 'df_fv',
                 'df_sac', 'df_scc', 'df_sav', 'df_scv')

for(d in data_frames){
  print(d)
  assign(d, df)
}

list_of_dfs <- list(df_mc, df_mv, df_fc, df_fv,
                    df_sac, df_scc, df_sav, df_scv)

```

#Fill number of blocks in real data
```{r}

list_of_values <- vector()

for(i in 1:length(traits)){
  
  current_t <- p_nogrm_true %>%
  filter(.[1] == traits[i]) %>%
  as.numeric(.[1,2:1683]) %>%
  na.omit(.)
  
  trait_p_0.001 <- length(current_t[current_t <= 0.001])
  trait_p_0.01 <- length(current_t[current_t <= 0.01])
  trait_p_0.05 <- length(current_t[current_t <= 0.05])
  trait_p_0.1 <- length(current_t[current_t <= 0.1])
  
  current_t_q <- qvalue(current_t)$qvalues
  
  trait_q_0.1 <- length(current_t_q[current_t_q <= 0.1])
  trait_q_0.2 <- length(current_t_q[current_t_q <= 0.2])
  trait_q_0.3 <- length(current_t_q[current_t_q <= 0.3])
  
  list_of_dfs[[i]]$num_blocks_real_data <- c(list_of_values, trait_p_0.001, trait_p_0.01, trait_p_0.05, trait_p_0.1,
                      trait_q_0.1, trait_q_0.2, trait_q_0.3)
  
}
```

#Fill proportion of permutations with as many or more blocks
```{r}
perm_no <- length(grm_p$X1)/8

for(i in 1:length(traits)){
  
  current_trait_df <- grm_p %>%
    filter(grm_p[2] == traits[i])
  
  
  trait_p_0.001 <- vector(length = perm_no)
  trait_p_0.01 <- vector(length = perm_no)
  trait_p_0.05 <- vector(length = perm_no)
  trait_p_0.1 <- vector(length = perm_no)
  
  trait_q_0.1 <- vector(length = perm_no)
  trait_q_0.2 <- vector(length = perm_no)
  trait_q_0.3 <- vector(length = perm_no)
  
  for(perm in 1:nrow(current_trait_df)){
    
    temp <- as.numeric(current_trait_df[perm,3:1684])
    temp_q <- qvalue(as.numeric(current_trait_df[perm,3:1684]))$qvalues
  
    trait_p_0.001[perm] <- length(temp[temp <= 0.001])
    trait_p_0.01[perm] <- length(temp[temp <= 0.01])
    trait_p_0.05[perm] <- length(temp[temp <= 0.05])
    trait_p_0.1[perm] <- length(temp[temp <= 0.1])
    
    trait_q_0.1[perm] <- length(temp_q[temp_q <= 0.1])
    trait_q_0.2[perm] <- length(temp_q[temp_q <= 0.2])
    trait_q_0.3[perm] <- length(temp_q[temp_q <= 0.3])
    
  }
  
  list_perm_results <- list(trait_p_0.001, trait_p_0.01, trait_p_0.05, trait_p_0.1, 
                            trait_q_0.1, trait_q_0.2, trait_q_0.3)
  
  num_to_compare <- list_of_dfs[[i]]$num_blocks_real_data
  
  #Fill proportion of permutations with as many or more blocks
  list_of_dfs[[i]]$prop_perm_blocks_as_many_or_more <- c(round(length(trait_p_0.001[trait_p_0.001 >= num_to_compare[1]])/perm_no, 3),
                                                     round(length(trait_p_0.01[trait_p_0.01 >= num_to_compare[2]])/perm_no, 3),
                                                     round(length(trait_p_0.05[trait_p_0.05 >= num_to_compare[3]])/perm_no, 3),
                                                     round(length(trait_p_0.1[trait_p_0.1 >= num_to_compare[4]])/perm_no, 3),
                                                     round(length(trait_q_0.1[trait_q_0.1 >= num_to_compare[5]])/perm_no, 3),
                                                     round(length(trait_q_0.2[trait_q_0.2 >= num_to_compare[6]])/perm_no, 3),
                                                     round(length(trait_q_0.3[trait_q_0.3 >= num_to_compare[7]])/perm_no, 3))
  
  # Get mean number of blocks across permutations                                         
  list_of_dfs[[i]]$mean_num_perm_blocks <- c(round(mean(trait_p_0.001), 0), round(mean(trait_p_0.01), 0),
                                             round(mean(trait_p_0.05), 0), round(mean(trait_p_0.1), 0),
                                             round(mean(trait_q_0.1), 0), round(mean(trait_q_0.2), 0),
                                             round(mean(trait_q_0.3), 0))
  
  # Get median number of blocks across permutations
  list_of_dfs[[i]]$median_num_perm_blocks <- c(median(trait_p_0.001), median(trait_p_0.01), median(trait_p_0.05),
                                               median(trait_p_0.1), median(trait_q_0.1), median(trait_q_0.2),
                                               median(trait_q_0.3))
  
  # Get nth percentile value of blocks at each threshold for n = {2.5, 5, 95, 97.5} from permutations
  percentiles <- lapply(list_perm_results, quantile, probs = c(.025, 0.05, 0.95, 0.975 ))
  
  for(a in 1:length(list_perm_results)){
    list_of_dfs[[i]]$percentile_2.5_perm[a] <- round(percentiles[[a]][1], 0)
    list_of_dfs[[i]]$percentile_5_perm[a] <- round(percentiles[[a]][2], 0)
    list_of_dfs[[i]]$percentile_95_perm[a] <- round(percentiles[[a]][3], 0)
    list_of_dfs[[i]]$percentile_97.5_perm[a] <- round(percentiles[[a]][4], 0)
  }
  
}

list_of_dfs[[1]]
```

#Name columns in data.frame
```{r}
name_columns <- function(x){
  
  colnames(x) <- c('Criteria', 'Number of blocks in the real data', 
'Proportion of permutations with as many or more blocks', 'Mean number of blocks across permutations',
  'Median number of blocks across permutations', '2.5 percentile value', '5 percentile value', 
  '95 percentile value', '97.5 percentile value')
}

lapply(list_of_dfs, name_columns)


```

```{r}
file_names <- c('male_cage_table.csv', 'male_vial_table.csv', 'female_cage_table.csv', 'female_vial_table.csv',
                'sa_cage_table.csv', 'sc_cage_table.csv', 'sa_vial_table.csv', 'sc_vial_table.csv')

for(file in 1:length(list_of_dfs)){
  
  write_csv(list_of_dfs[[file]], path = file_names[file], col_names = TRUE)
  
}
```
